\documentclass[review]{elsarticle}
%% Latex documents that need direct input
\input{latex/filesystem/package_basic.tex}    % contains the latex packages
\input{latex/filesystem/package_edition.tex}  % packages to facilitate editing
\input{latex/filesystem/fileSetup.tex}        % contains package and variables init.
\input{content/acronym_definition.tex}        % contains the acronims

%% Select inputing only one part of the document
%\includeonly{content/intro/intro}   % the file wihtout .tex
%\includeonly{content/other/other_content}

% \addbibresource{./content/lit_review.bib}
% \addbibresource{./content/biblatex-examples.bib}

\begin{document}

% Abstract and keywords are in frontmatter in this template
\input{content/frontmatter.tex}               % contains the Title and Autor info
\maketitle

\linenumbers
%% Incldue the content without .tex extension
%\acresetall  % reset the acronyms from the abstract
\acresetall  % reset the acronyms from the abstract
\input{content/intro/intro}          % the file wihtout .tex
\input{content/survey/background}    % the file wihtout .tex
\input{content/method/method}
\input{content/experiment/experiment}
\input{content/experiment/discussion}

%\input{content/results/results}

\section{Conclusions}\label{sec:con}
The work presented here addresses automatic classification of \ac{sdoct} volumes as normal or \ac{dme}.
In this regard, an extensive study is carried out covering the
(i) effects of different pre-processing steps, 
(ii) influence of different mapping and feature extraction strategies,
(iii) impact of the codebook size in \ac{bow}, and
(iv) comparison of different classification strategies.

While outperforming the previous studies~\cite{Lemaintre2015miccaiOCT,Venhuizen2015}, the obtained results in this research showed the impact and importance of optimal codebook size, the potential of 3D features and high level representation of 2D features while extracted from local patches.
The strength of \ac{svm} classifier while used along \ac{bow} approach and \ac{rf} classifier while used with global mapping.
In terms of pre-processing steps, although the highest performances are achieved while alignment and flattening were used in the pre-processing, it was shown that the effects of these extra steps are not consistent for all the cases and do not guaranty a better performance.

{\color{red} AVENUES FOR FUTURE WORK
\begin{itemize}
  \item the flattening is not perfect, we could do it better
  \item study LBP as with no rotation invariance that could help to have more discriminative patterns
  \item include over feature as gradient or something else that could be complementary to the LBP
\end{itemize}}

\section*{Acknowledgments}\label{sec:acknowledgements}

This project was supported by the Singapore French Institute (IFS) and the Singapore Eye Research Institute (SERI) through the PHC Merlion program (2015-2016) and the Regional Council of Burgundy (grant nb. 2015-9201AAO050S02760).
Calculations were performed using HPC resources from DSI-CCUB (Universit\'e de Bourgogne).

%The obtained results in this resarch, showed clear improvement with respect to the previous studies\cite{Lemaintre2015miccaiOCT,Venhuizen2015}
%Table~\ref{tab:results_summary} summarizes the most relevant aspects of all the experimentations, 
%showing a clear improvement with respect to previous studies~\cite{Lemaintre2015miccaiOCT,Venhuizen2015}.
%Based on the reported results, the 3D features and high-level representation of 2D features using patches achieve the best results.

%\input{content/experiment/Table5.tex}
%\section{Future work }
%TOMORROW THE MOON !!

\section*{Conflict of interest statement}

The authors declare no conflict of interest.

\begin{appendices}
\section{Complementary results for \emph{Experiment~\#1~\&~\#2~\&~\#3}}\label{app:1}
\input{content/experiment/Table2}
\input{content/experiment/Table3}
\input{content/experiment/Table4}
\end{appendices}

% Our method is based on \ac{lbp} features to describe the texture of \ac{oct} images and we compare different \ac{lbp} features extraction approaches to compute a single signature for the whole \ac{oct} volume.

\section*{References}
\bibliography{./content/literature_review}   %>>>> bibliography data in report.bib

\end{document}
